Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-23 Report/conclusions.tex
final_submission_text

In this paper, we addressed the allocation of space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{OFDM} system. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user can be achieved by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint as a sequence of convex subsets to design the precoders for minimizing the number of queued packets. Additionally, an alternative approach using \ac{MSE} relaxation is also proposed with the same objective by fixing the receivers based on \ac{MSE} minimization. We also proposed the distributed solutions for the centralized \ac{JSFRA} problem using \ac{ADMM} and primal decomposition methods. Finally, we proposed an iterative algorithm to determine the precoders in a decentralized manner based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme. Numerical results shows that the proposed algorithms perform better than the existing approaches.

>>>>

In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint by a sequence of convex subsets to design the precoders for minimizing the total number of queued packets in the system. In addition to that, an alternative method using \ac{MSE} relaxation is also proposed using the same objective by fixing the receivers based on the \ac{MMSE} criterion. Then we proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods. At last, we proposed a practical iterative algorithm to evaluate the precoders in a decentralized manner by solving the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme. The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the precoders to minimize the total number of backlogged packets. Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.

### 2014-10-23 Report/introduction.tex
final_submission_text

In this paper, we consider the problem of precoder design across the space-frequency resources to minimize the total number of queued packets waiting in all \acp{BS}. For this highly nonconvex problem, we first propose two centralized methods. In the first method, we relax the nonconvex constraint by the first order Taylor approximation around an operating point, which is updated in an iterative manner until convergence or to a certain accuracy. In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders. For a distributed implementation, we further propose decentralized approaches based on primal and \ac{ADMM} schemes to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul. We also propose an iterative algorithm by solving the \ac{KKT} equations, which can be implemented efficiently in a distributed manner.

>>>>

\subsubsection*{Main Contributions}
In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}. Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations. Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.

### 2014-10-23 Report/kkt_mse_approach.tex
final_submission_text

The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as

>>>>

The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as
